---
title: "R Notebook"
output: html_notebook
---

# Libraries and paths
```{r}

rm(list=ls())
base.path= "C:/Users/daksh/OneDrive/Documents/july_2024_internship" #/data/data_cleaned_Batch1.RData"
source(file.path(base.path,'scripts','fit_behaviour.R')) # fit choices for each single subject with model
saveFolder <- file.path(base.path, "Results", "RL_models", "Self_other_phase", "Model1")
model.name <- "model1"
```


```{r}
library(rstan)
library(rstantools)
library(dplyr)
library(tidyverse)
library(ggpubr)
library(psych)
library(brms)
library(ggcorrplot)
library(sjPlot)
library(doParallel)
library(rmcorr)
library(knitr)
library(stargazer)
```


```{r}
# Source the fit_behaviour function
source(file.path(base.path, 'scripts', 'fit_behaviour.R'))

# Compile the stan model
#model.code <- stan_model(file = file.path(base.path, "scripts", "RL_M1.stan"))
```


Say your folders are:
- Data
- Scripts
- Results

Then you have 
Results > RL_models > Self_other_phase> Model1 > files: model1_participant1.RData, model1_participant2.RData


#load my data

```{r}
# Define the path to your data file
data_file <- "C:/Users/daksh/OneDrive/Documents/july_2024_internship/data/data_cleaned_Batch1.RData"

# Load the data
load(data_file)
```


```{r}
df <- data.cleaned %>%
  dplyr::rename(RateSelf=rate_self, RateOther=rate_other) %>% # change all the variable names so that they are what the stan model expects
  dplyr::mutate( active_trial   = as.numeric(self_feedback == 0))
```

```{r}
# Filter data for Phase 1
df_phase1 <- df %>% filter(phase == 1 & player_mu_drift==0)

# Define the participants vector based on unique player IDs in phase 1
participants <- unique(df_phase1$ID)
```

```{r}

# in the future: loop over models
model.name = 'RL_M1'
stan_file <- file.path(base.path, 'scripts', paste0(model.name, ".stan"))
my.model <- stan_model(file = stan_file)
saveFolder <- file.path(base.path, "Results", "RL_models", "Self_other_phase", "Model1")
dir.create(saveFolder, recursive = TRUE)

# Fit the model for each participant in Phase 1
for (iparticipant in participants) {
  # Subset data for the current participant
  df_participant <- df_phase1 %>% filter(ID == iparticipant) %>%
    dplyr::select(ID, RateSelf, RateOther, active_trial, control_level, feedback, phase_trial)  
  
  # Prepare the data list for Stan model
  stan_data <- list(
    ntr = nrow(df_participant),
    ntr_phase = max(df_participant$phase_trial),
    nrow = nrow(df_participant),
    RateSelf = df_participant$RateSelf,
    RateOther = df_participant$RateOther,
    active_trial = df_participant$active_trial,
    control_level = df_participant$control_level,
    feedback = df_participant$feedback,
    phase_trial = df_participant$phase_trial
  )
  
  # Define export file path
  export.file <- file.path(saveFolder, paste0(model.name, '_subj', iparticipant, '.RData'))
  print(export.file)
  
  # Check if the file already exists so that if we fit many people and it crashes in the middle, we can start again where we stopped (or later we could also use parallel loops)
  if (!file.exists(export.file)) {
    # Fit the model for the current participant
    out <- fit_behaviour(stan_data, my.model, 'sampling')
    fit.results=out$singleSessionParas
    fit.results$fitted.ok.flag=out$fitted.ok.flag
    fit.results$ID= iparticipant
   # browser() # make sure that you have whether it fitted ok or not, the ID of the participant and the parameters that are defined in the stan model 
    # Save the results to disk
    save(fit_results, file = export.file)
   # browser()
  }
}

print("Model fitting completed for all participants in Phase 1.")

```


```{r}
# Fit the model for each participant in Phase 1
overwrite <- TRUE  # Set to TRUE if you want to overwrite existing files, FALSE otherwise

for (iparticipant in participants) {
  # Subset data for the current participant
  df_participant <- df_phase1 %>% filter(ID == iparticipant) %>%
    dplyr::select(ID, RateSelf, RateOther, active_trial, control_level, feedback, phase_trial)  
  
  # Prepare the data list for Stan model
  stan_data <- list(
    ntr = nrow(df_participant),
    ntr_phase = max(df_participant$phase_trial),
    nrow = nrow(df_participant),
    RateSelf = df_participant$RateSelf,
    RateOther = df_participant$RateOther,
    active_trial = df_participant$active_trial,
    control_level = df_participant$control_level,
    feedback = df_participant$feedback,
    phase_trial = df_participant$phase_trial
  )
  
  # Define export file path
  export.file <- file.path(saveFolder, paste0(model.name, '_subj', iparticipant, '.RData'))
  print(paste("Saving to:", export.file))
  
  # Check if the file already exists and if we want to overwrite it
  if (!file.exists(export.file) || overwrite) {
    # Fit the model for the current participant
    out <- fit_behaviour(stan_data, my.model, 'sampling')
    fit.results = out$singleSessionParas
    fit.results$fitted.ok.flag = out$fitted.ok.flag
    fit.results$ID = iparticipant
    print(paste("Saving fit.results for participant", iparticipant))
    print(head(fit.results))  # Print a sample to check
    # Save the results to disk
    save(fit.results, file = export.file)
  }
}

print("Model fitting completed for all participants in Phase 1.")

```
```{r}
# Fit the model for each participant in Phase 1
overwrite <- TRUE  # Set to TRUE if you want to overwrite existing files, FALSE otherwise

for (iparticipant in participants) {
  # Subset data for the current participant
  df_participant <- df_phase1 %>% filter(ID == iparticipant) %>%
    dplyr::select(ID, RateSelf, RateOther, active_trial, control_level, feedback, phase_trial)  
  
  # Prepare the data list for Stan model
  stan_data <- list(
    ntr = nrow(df_participant),
    ntr_phase = max(df_participant$phase_trial),
    nrow = nrow(df_participant),
    RateSelf = df_participant$RateSelf,
    RateOther = df_participant$RateOther,
    active_trial = df_participant$active_trial,
    control_level = df_participant$control_level,
    feedback = df_participant$feedback,
    phase_trial = df_participant$phase_trial
  )
  
  # Define export file path
  export.file <- file.path(saveFolder, paste0(model.name, '_subj', iparticipant, '.RData'))
  print(paste("Saving to:", export.file))
  
  # Check if the file already exists and if we want to overwrite it
  if (!file.exists(export.file) || overwrite) {
    # Fit the model for the current participant
    out <- fit_behaviour(stan_data, my.model, 'sampling')
    if (!is.null(out$singleSessionParas)) {
      fit.results = out$singleSessionParas
      fit.results$fitted.ok.flag = out$fitted.ok.flag
      fit.results$ID = iparticipant
      print(paste("Saving fit.results for participant", iparticipant))
      print(head(fit.results))  # Print a sample to check
      # Save the results to disk
      save(fit.results, file = export.file)
    } else {
      print(paste("Model fitting failed for participant", iparticipant))
    }
  } else {
    print(paste("File already exists for participant", iparticipant))
  }
}

print("Model fitting completed for all participants in Phase 1.")
```



# Illustrate data

```{r}
# Load necessary libraries for data visualization and summary
library(ggplot2)
library(dplyr)
library(psych)

# Summarize the data
summary(df)

# Summary statistics for numeric columns
describe(df)

```

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)
library(psych)
library(ggcorrplot)


# Histogram of RateSelf
ggplot(df, aes(x = RateSelf)) +
  geom_histogram(binwidth = 0.5, fill = 'blue', color = 'black', alpha = 0.7) +
  labs(title = 'Histogram of RateSelf', x = 'rate_self', y = 'Frequency')

# Boxplot of RateSelf by Player ID
ggplot(df, aes(x = ID, y = RateSelf, fill = ID)) +
  geom_boxplot() +
  labs(title = 'Boxplot of RateSelf by Player ID', x = 'Player ID', y = 'rate_self') +
  theme(legend.position = 'none')

# Calculate the correlation matrix
cor_matrix <- df %>%
  select(RateSelf, RateOther, control_level, feedback) %>%
  cor()

# Plot the correlation matrix
ggcorrplot(cor_matrix, lab = TRUE)

```



# Fit phase 1 models

I9n the fit_behaviour code, change:
  my.adapt_delta=0.8 # setting for first iteration
  my.iter=4000 # setting for first iteration
```{r} 
#old code#
# from the data frame of the whole experiment, take only the columns you  need and only phase 1 and only the trials before there is a sudden change (for all 4 games)
# the columns you need are what you have as input in Stan

# compile the stan model
model.code=stan_model(file=file.path(base.path,'scripts','RL_M1.stan'))

for (iparticipant in participants){ # loop over participants

  # create a file where you will store the output of the modeling
  
  
export.file=file.path(saveFolder,paste0(model.name,'_',unique(df$ID),'_TestDay',unique(df$test_day),'_',dataset,'.RData'))
print(export.file)
if (!file.exists(export.file)){ 
  # from the 'big' data frame, take out the data just for that person
  out = fit_behaviour_1(df,model.code,'sampling')
  # append ID etc.
   # store the file to disk (using save command)
}
}
```

# Simulations phase 1
##Data Prep
```{r}
# Define the path to the folder containing the saved RData files
saveFolder <- file.path(base.path, "Results", "RL_models", "Self_other_phase", "Model1")

# List all RData files in the directory
file_list <- list.files(path = saveFolder, pattern = "*.RData", full.names = TRUE)

# Print the list of files being matched
print("List of files to load:")
print(file_list)

# Initialize an empty list to store the loaded data
all_data <- list()

# Loop through each file and load the data
for (file in file_list) {
  print(paste("Loading file:", file))  # Print which file is being loaded
  load(file)  # This will load 'fit.results' into the environment
  
  # Check if 'fit.results' is loaded correctly
  if (exists("fit.results")) {
    print(paste("Successfully loaded data from:", file))
    print(head(fit.results))  # Print the first few rows of fit.results to check
    # Append the loaded data to the list
    all_data[[length(all_data) + 1]] <- fit.results
  } else {
    print(paste("Error loading data from file:", file))
  }
}

# Combine all data into a single data frame
combined_data <- do.call(rbind, all_data)

# Print the combined data to check
print("Combined data head:")
print(head(combined_data))
print("Combined data tail:")
print(tail(combined_data))

# Check for missing participants
loaded_participants <- unique(combined_data$ID)
missing_participants <- setdiff(participants, loaded_participants)
print("Missing participants:")
print(missing_participants)
```

## Generate/simulate parameters then choices
- package saving to disk: for each agent a file with the choices and columns also for the parameters used to make the choices

```{r}
library(rstan)
library(dplyr)

# Define the number of simulated agents and days
n.simul.agents <- 200
#num_trials <- 100  # Set the number of trials

# Get min and max values of each parameter from the original data
param_min_max <- combined_data %>% 
  summarise(
    rating_noise_min = min(rating_noise), rating_noise_max = max(rating_noise),
    learning_rate_min = min(learning_rate), learning_rate_max = max(learning_rate),
    prior_self_min = min(prior_self), prior_self_max = max(prior_self),
    prior_other_min = min(prior_other), prior_other_max = max(prior_other)
  )

# Prepare the data list for simulation
# df.list <- list(
#   ntr = num_trials,
#   ntr_phase = 10,
#   nrow = num_trials,
  # active_trial = sample(0:1, num_trials, replace = TRUE),
  # control_level = runif(num_trials),
  # feedback = rnorm(num_trials),
  # phase_trial = rep(1:10, length.out = num_trials)
#)

# Compile the simulation model
sim_model_name <- 'RL_M1_simulations'
sim_stan_file <- file.path(base.path, 'scripts', paste0(sim_model_name, ".stan"))
sim_model <- stan_model(file = sim_stan_file)

# Initialize an empty list to store the simulated data
sim_data_list <- list()

# Run the Stan model for each simulated agent and save the results
good.schedule.IDs=c(1,33) # take 2: 1 that does not have active trials and one that has a median amount - chosen from the real data
for (i in 1:n.simul.agents) {
  # pick a random schedule
  this.ID.forSchedule=sample(good.schedule.IDs,1)
  this.df = df %>% dplyr::filter(phase==1 &player_mu_drift==0 & ID==this.ID.forSchedule) %>%
    dplyr::select(active_trial,control_level,feedback,phase_trial)
  df.list <- as.list(this.df)
  #df.list$ntr = nrow(this.df)
  df.list$ntr_phase = max(this.df$phase_trial)
  df.list$nrow = nrow(this.df)
  # Update the data list with simulated parameters
  df.list$rating_noise <- runif(1, param_min_max$rating_noise_min, param_min_max$rating_noise_max)
  df.list$learning_rate <- runif(1, param_min_max$learning_rate_min, param_min_max$learning_rate_max)
  df.list$prior_self <- runif(1, param_min_max$prior_self_min, param_min_max$prior_self_max)
  df.list$prior_other <- runif(1, param_min_max$prior_other_min, param_min_max$prior_other_max)
  
  # Simulate choices using the Stan model
  simChoices <- sampling(sim_model, data = df.list, chains = 1, iter = 1, algorithm = 'Fixed_param', refresh = 0)
  
  # Extract and save the simulated choices
  choices <- as.data.frame(lapply(rstan::extract(simChoices, pars = c("RateSelf", "RateOther")), colMeans))
 
  
  # Save the simulated choices and parameters to disk
  sim_save_file <- file.path(saveFolder, paste0("sim_agent_", i, ".RData"))
  sim_data <- cbind(choices, rating_noise = df.list$rating_noise, learning_rate = df.list$learning_rate, prior_self = df.list$prior_self, prior_other = df.list$prior_other)
  
   sim_data_list[[i]] <- cbind(sim_data,this.df)
  
  save(sim_data, file = sim_save_file)
}

# Combine all simulated data into one data frame - SAVE TO FILE AND ALSO WITH AN IF ONLY IF IT DOESNT EXIST and save together with sim params OR we can later get sim params from this
sim_combined_data <- do.call(rbind, sim_data_list)

save(sim_combined_data, file = "C:/Users/daksh/OneDrive/Documents/july_2024_internship/data/sim_combined_data.RData")

# Print the combined simulated data
print(sim_combined_data)
```

## Fit the simulated choices
- store the fitted parameters, but together with a copy of the simulated parameters (e.g. rating.noise.fitted, rating.noise.simulated)

```{r}
# Compile the Stan model for simulations
sim_model_name <- 'RL_M1'#    _simulations'
sim_stan_file <- file.path(base.path, 'scripts', paste0(sim_model_name, ".stan"))
sim_model <- stan_model(file = sim_stan_file)

# load the simulated choices here (sim_combined_data)

sim_combined_data_file <- "C:/Users/daksh/OneDrive/Documents/july_2024_internship/data/sim_combined_data.RData"
load(sim_combined_data_file)
sim_fitted_params <- list()

for (i in 1:num_sim_agents) {
  sim_data <- sim_data_list[[i]]
  
  # Prepare the data list for Stan model
  stan_data <- list(
   # nrow = nrow(sim_data),
    ntr_phase = max(sim_data$phase_trial),
    nrow = nrow(sim_data),
    RateSelf = sim_data$RateSelf,
    RateOther = sim_data$RateOther,
    active_trial = sim_data$active_trial,
    control_level = sim_data$control_level,
    feedback = sim_data$feedback,
    phase_trial = sim_data$phase_trial
  )
  
  # Fit the model
  out <- fit_behaviour(stan_data, sim_model, 'sampling')
  fit.results <- out$singleSessionParas
  fit.results$fitted.ok.flag <- out$fitted.ok.flag
  
  # Store the results along with simulated parameters
  #fit.results <- cbind(fit.results, sim_params[i, ])
  simulated.pars = sim_data %>% dplyr::select(rating_noise, learning_rate, prior_self, prior_other) %>% distinct()
  names(simulated.pars) = paste0('sim.',names(simulated.pars))
  fit.results <- cbind(fit.results, simulated.pars) #sim_params[i, ])
  
  
  sim_fitted_params[[i]] <- fit.results
  
  # Save the fitted results to disk
  fit_save_file <- file.path(saveFolder, paste0("fit_sim_agent_", i, ".RData"))
  save(fit.results, file = fit_save_file)
}
 
# Combine all simulated fitted parameters into one data frame
sim_fitted_df <- do.call(rbind, sim_fitted_params)

```

## Compare simulated and fitted parameters
using tab_corr from sjPlot
and also do scatter plots

```{r}
# Load necessary libraries
if (!requireNamespace("sjPlot", quietly = TRUE)) {
  install.packages("sjPlot")
}

library(sjPlot)
library(dplyr)
library(ggplot2)

# Extract the simulated and fitted parameters
params <- sim_fitted_df %>%
  dplyr::select(rating_noise, learning_rate, prior_self, prior_other, 
                sim.rating_noise, sim.learning_rate, sim.prior_self, sim.prior_other)

# Rename columns for clarity
colnames(params) <- c("fitted_rating_noise", "fitted_learning_rate", "fitted_prior_self", "fitted_prior_other",
                      "simulated_rating_noise", "simulated_learning_rate", "simulated_prior_self", "simulated_prior_other")

# Plotting function for scatter plots with fitted line
plot_scatter <- function(fitted, simulated, param_name) {
  ggplot(params, aes_string(x = simulated, y = fitted)) +
    geom_point(color = "black") +
    geom_smooth(method = "lm", color = "red") +
    labs(title = paste("Scatter Plot of", param_name, "(Simulated vs Fitted)"),
         x = paste("Simulated", param_name),
         y = paste("Fitted", param_name)) +
    theme_minimal()
}

# Create and display scatter plots for each parameter
p1 <- plot_scatter("fitted_rating_noise", "simulated_rating_noise", "Rating Noise")
print(p1)

p2 <- plot_scatter("fitted_learning_rate", "simulated_learning_rate", "Learning Rate")
print(p2)

p3 <- plot_scatter("fitted_prior_self", "simulated_prior_self", "Prior Self")
print(p3)

p4 <- plot_scatter("fitted_prior_other", "simulated_prior_other", "Prior Other")
print(p4)

# Correlation table
table_1 <- tab_corr(params, title = "Correlation Table of Simulated and Fitted Parameters")
table_1
```


# B
#need to edit the code from above to reflect the fact that we're now using real participants' parameters



```{r}
# Load necessary libraries
library(rstan)
library(dplyr)

# Define paths
base.path <- "C:/Users/daksh/OneDrive/Documents/july_2024_internship"
saveFolder <- file.path(base.path, "Results", "RL_models", "Self_other_phase", "Model1")

# Load the real participant data
data_file <- "C:/Users/daksh/OneDrive/Documents/july_2024_internship/data/data_cleaned_Batch1.RData"
load(data_file)

df <- data.cleaned %>%
  dplyr::rename(RateSelf = rate_self, RateOther = rate_other) %>%
  dplyr::mutate(active_trial = as.numeric(self_feedback == 0))

# Filter data for Phase 1
df_phase1 <- df %>% filter(phase == 1 & player_mu_drift == 0)

# Define the participants vector based on unique player IDs in phase 1
participants <- unique(df_phase1$ID)

# Compile the Stan model for real participants
real_model_name <- 'RL_M1_simulations'
real_stan_file <- file.path(base.path, 'scripts', paste0(real_model_name, ".stan"))
real_model <- stan_model(file = real_stan_file)

# Initialize an empty list to store the fitted parameters
real_fitted_params <- list()

for (iparticipant in participants) {
  # Subset data for the current participant
  df_participant <- df_phase1 %>% filter(ID == iparticipant) %>%
    dplyr::select(ID, RateSelf, RateOther, active_trial, control_level, feedback, phase_trial)  
  
  # Prepare the data list for Stan model
  stan_data <- list(
    ntr_phase = max(df_participant$phase_trial),
    nrow = nrow(df_participant),
    RateSelf = df_participant$RateSelf,
    RateOther = df_participant$RateOther,
    active_trial = df_participant$active_trial,
    control_level = df_participant$control_level,
    feedback = df_participant$feedback,
    phase_trial = df_participant$phase_trial
  )
  
  # Fit the model for the current participant
  out <- sampling(real_model, data = stan_data, chains = 1, iter = 1, algorithm = 'Fixed_param', refresh = 0)
  fit_results <- as.data.frame(rstan::extract(out, permuted = TRUE))
  fit_results$fitted.ok.flag <- ifelse(nrow(fit_results) > 0, 1, 0)
  fit_results$ID <- iparticipant
  
  # Store the results
  real_fitted_params[[length(real_fitted_params) + 1]] <- fit_results
  
  # Define export file path
  export_file <- file.path(saveFolder, paste0("real_participant_", iparticipant, ".RData"))
  
  # Save the results to disk
  save(fit_results, file = export_file)
}

# Combine all fitted parameters into one data frame
real_fitted_df <- do.call(rbind, real_fitted_params)

# Save the combined data frame to disk
save(real_fitted_df, file = file.path(base.path, "data", "real_fitted_df.RData"))

# Print the combined fitted data
print(real_fitted_df)
```

- 4 plots: ratings over time, for each time point mean and standard error across participants. and then add mean and standard error of the model (different colour - or plot it as a line). in theory could add individual participants as dots (but maybe very busy)

- one plot that is just the first trial in each game as mean and standard error, also show individual participants as little dots + show the model predictions. + a line joining the data from each person.
